---
title: "final_project2"
output: html_document
---

First, I will include the all the necessary data in the chunks separately, because I have a lot of data to go through. 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

setwd("C:\\krishna\\college\\SPRING 2022\\insh2102\\finalproject\\")

library(sf)
library(PROJ)

map <- read.csv("map.csv",stringsAsFactors=F)
head(map)

canopy_change_spdf <- st_read("Canopy_Change_Assessment%3A_Heat_Metrics.shp")
head(canopy_change_spdf)



```

```{r}

#canopy_tree$TC_E_A[ which(canopy_tree$TC_E_A == 0)] <- NA
ggplot(canopy_tree)
  geom_sf() + 
  aes(fill=canopy_tree$TC_E_P) + 
  scale_fill_gradient2(midpoint=51600,low = "blue",high="red",mid="white") +
  labs(fill = "Log pop") +
  theme_void()

```

```{r}
library(rlang)
filter1 <- quos(Sector = "Commercial",
                Source = "Gasoline")
filter2 <- quos(Sector = "Commercial",
                Source = "Gasoline")
```

```{r}
week_boston_air_quality <- read.csv("week-boston-air-quality.csv", stringsAsFactors= F)
week <- table(week_boston_air_quality$AQI)

month_boston_air_quality <- read.csv("month-boston-air-quality.csv", stringsAsFactors= F)
month <- table(month_boston_air_quality$AQI)

barplot(week, main = "Weekly Boston Air Quality")
barplot(month, main = "Monthly Boston Air Quality")

```
From this we can tell that Boston hasn't really had problems with the air quality in the past month. Reaching a maximum of 47 at most 2 times in the month of April 2022, the air quality has always been in the green zone. This means that overall Boston does not really face issues of pollution. But, we have also seen a lot of articles pop-up about the heat islands created in boston
```{r}
library(dplyr)
library(purrr)
library(ggplot2)

community_greenhouse_gas <-read.csv("community-greenhouse-gas.csv", stringsAsFactors= F)
local_government_operations_fuels <-read.csv("local-government-operations-fuels.csv", stringsAsFactors= F)
local_government_operations_greenhouse_gas <-read.csv("local-government-operations-greenhouse-gas.csv", stringsAsFactors= F)
```

```{r}
d<-community_greenhouse_gas[which(community_greenhouse_gas$Sector=="Commercial"& community_greenhouse_gas$Source=="Electricity")]
plot(c(2005,2006,2007,2008,2009,2010,2011,2012,2013,2014,2015,2016,2017,2018,2019), 
     c(1082796,1068737,1124786,1183985,1109123,1118167,1150003,1053562,1185444,1252271,1349883,1240286,1239513,1331914,1321707)
, xlab="Year", ylab="GHG Emissions(mt CO2e)", main="Commercial Natural Gas greenhouse gas emissions")
```
library(rlang)
filter1 <- filter(community_greenhouse_gas, community_greenhouse_gas$Sector=="Commercial" & community_greenhouse_gas$Source=="Electrical")
ggplot(filter1) + 
  geom_point() +
  aes(x=Year.Calendar.Year.,y=GHG.Emissions.mt.CO2e.)


```

library(ggplot2)
library(leaflet)
library(RColorBrewer)
library(classInt)

breaks_qt <- classIntervals(c(min(canopy_change_spdf$Mean_p2_T_) - .00001, canopy_change_spdf$Mean_p2_T_), n = 7, style = "quantile")

p_popup <- paste0("<strong>Mean Temperature density: </strong>", canopy_change_spdf$Mean_p2_T_)

pal_fun <- colorQuantile("YlOrRd", NULL, n = 5)


canopy_change_WGS84 <- st_transform(canopy_change_spdf, 4326)
leaflet(canopy_change_WGS84) %>%
  addPolygons(
    stroke = FALSE, 
    fillColor = ~pal_fun(Mean_p2_T_),
    fillOpacity = 0.5, smoothFactor = 0.5,
    popup = p_popup) %>%
  addTiles() %>%
  addLegend("bottomright", 
            colors = brewer.pal(7, "YlOrRd"), 
            labels = paste0("up to ", format(breaks_qt$brks[-1], digits = 2)),
            title =  'Mean temperature of area in a day')
```

``` {r}


```

